The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-09-18 paper.tex
Cleared a TODO about direction of sonority distance

The second generalisation is that the more sonorous the C\textsubscript{1}, the more likely
epenthesis is to occur. Let us fix the sonority distance between the two consonants of the cluster at -2, but vary their distance from V: %TODO : check if it should be -2 or +2

@@

In this paper, I proposed two desiderata for a metric of sonority contour distance, and suggested {\sc Sonority Angle} as a concrete metric that fit these criteria. In this section, I examine the weaknesses of {\sc Sonority Angle} as a metric, as well as possible extensions.

@@

%TODO : draw diagram showing what happens with the different C1's
\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
                      \node at (-3, 7.0) {Sonority}; % axis label
					 % left diagram
                      \draw (5,2) -- (0,4);
                      \draw (0,3) -- (5,6) ; % rising sonority
                      \node[left] at  (0,4) {r}; 
                      \node[left] at  (0,3) {n}; 
                      \node[right] at (5,2) {f};
                      \node[right] at (5,6) {\textipa{1}};
     \end{tikzpicture}

@@

\noindent {\bf Why these vectors?} In the sonority contour faithfulness approach, the relevant comparison is between C1-C2 and C1-V. But why these two vectors? In particular, why not C1-C2 versus V-C2?

>>>>

The second generalisation is that the more sonorous the C\textsubscript{1}, the more likely
epenthesis is to occur. Let us fix the sonority distance between the two consonants of the cluster at 2, but vary their distance from V:

@@

In this paper, I proposed two desiderata for a metric of sonority contour distance, and suggested {\sc Sonority Angle} as a concrete metric that fit these criteria. In this section, I examine first a general question regarding sonority contour faithfulness, then discuss weaknesses of {\sc Sonority Angle} as a metric, as well as possible extensions of this metric to domains beyond sonority-driven epenthesis.

\section{Disregarding V-C2}

In the sonority contour faithfulness approach, the relevant comparison is between C1-C2 and C1-V. But why these two vectors? In particular, why not C1-C2 versus V-C2?

@@

\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
                      \node at (-3, 7.0) {Sonority}; % axis label
					 % left diagram
                      \draw (5,2) -- (0,4);
                      \draw (0,3) -- (5,6) ; % rising sonority
                      \node[left] at  (0,4) {r}; 
                      \node[left] at  (0,3) {n}; 
                      \node[right] at (5,2) {f};
                      \node[right] at (5,6) {\textipa{1}};
     \end{tikzpicture}

@@
